Deep Reinforcement Learning for Conservation Decisions

### 2020-12-04 manuscript/manuscript.Rmd
gym_fishing example

---
title: Deep Reinforcement Learning for Conservation Decisions
authors:
  - name: Carl Boettiger
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: cboettig@berkeley.edu

@@

```{r setup, cache = FALSE}
library(tidyverse)
library(reticulate)
```

@@

# train an agent (model) on one of the environments:
env <- gym$make("fishing-v1")
a2c <- sb3$A2C('MlpPolicy', env, verbose=0L) # Must use L for integers!
a2c$learn(total_timesteps=300000L)
sims <- env$simulate(a2c, reps = 500L)
```

```{r}
sims %>%
  group_by(time) %>% 
  summarise(ave_state = mean(state),
            sd_state = sd(state),
            ave_action = mean(action),
            ave_reward = mean(reward),
            .groups = "drop") %>%
  ggplot(aes(time, ave_state)) +  geom_line()

```

```{r}
sims %>% filter(rep < 50) %>% ggplot(aes(time, state, group = as.factor(rep))) + geom_line(alpha=0.1)
```

```{r}
policy <- env$policyfn(a2c, reps = 50L)
policy %>% ggplot(aes(state, action, group=rep)) + geom_point()
```

>>>>

---
title: Deep Reinforcement Learning for Conservation Decisions
authors:
  - name: Marcus Lapeyrolerie
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
  - name: Melissa Chapman
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
  - name: Kari Norman
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
  - name: Carl Boettiger
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: cboettig@berkeley.edu

@@

```{r setup, cache = FALSE, include = FALSE}
library(tidyverse)
library(patchwork)
library(reticulate)

knitr::opts_chunk$set(echo=FALSE)
```

@@

# train an agent (model) on one of the environments:
env <- gym$make("fishing-v1")
a2c <- sb3$A2C('MlpPolicy', env, verbose=0L, seed = 42L) # Must use L for integers!
a2c$learn(total_timesteps=300000L)
sims <- env$simulate(a2c, reps = 500L)
```

```{r}
fig_fish_sims <- sims %>% 
  filter(rep < 50) %>%
  ggplot(aes(time, state, group = as.factor(rep))) + geom_line(alpha=0.1)
policy <- env$policyfn(a2c, reps = 50L)
fig_fish_policy <- policy %>% ggplot(aes(state, state - action, group=rep)) + geom_point()
```

```{r fig1, fig.cap=""}
fig_fish_sims + fig_fish_policy
```
